\textbf{Title of Work}:  Plain English FILENAME: MPE.ZIP AUTHOR: Venerable H. Gunaratana Mahathera\\
\textbf{Publisher's Address}: H. Gunaratana Mahathera Bhavana Society Rt. 1 Box 218-3 High View, WV 26808. USA\\
\textbf{date of publication}: December 7, 1990 \\
\textbf{date of bodhinet release}: April 1994 \\
\textbf{origin}: Tiger Team Buddhist\\
Information Network (510) 268-0102 * BodhiNet (72:1000/658)\\
The publisher retains all rights to this work and hereby grants electronic distribution rights to BodhiNet Democratic Buddhist
Network. This work may be freely copied and redistributed, provided that it is accompanied by this Agreement and is distributed
at no cost to the recipient. If this work is used by a teacher in a class, or is quoted in a review, the publisher shall be notified of
such use.

If you find this work of value, please consider sending a donation to the author or publisher, so that these works may continue to
be made available.

BodhiNet 1920 Francisco St., Suite 112 Berkeley, CA 94709. USA
Tel. 510-540-6565 510-268-0102 Modem (via Tiger Team)

\newpage
\subsection*{About the Author}

Venerable Henepola Gunaratana was ordained at the age of 13 as a Buddhist monk
at a small temple in Malandeniya Village in Kurunegala District in Sri Lanka.
His preceptor was Venerable Kiribatkumbure Sonuttara Mahathera. At the age of 20
he was given higher ordination in Kandy in 1947. He received his education from
Vidyalankara College and Buddhist Missionary College in Colombo. Subsequently he
traveled to India for five years of missionary work for the Mahabodhi Society,
serving the Harijana (Untouchable) people in Sanchi, Delhi, and Bombay. Later he
spent ten years as a missionary in Malaysia, serving as religious advisor to the
Sasana Abhivurdhiwardhana Society, Buddhist Missionary Society and the Buddhist
Youth Federation of Malaysia.

He has been a teacher in Kishon Dial School and Temple Road Girls' School and
Principal of the Buddhist Institute of Kuala Lumppur.

At the invitation of the Sasana Sevaka Society, Venerable Gunaratana came to the
United States in 1968 to serve as Hon. General Secretary of the Buddhist Vihara
Society of Washington, D.C. In 1980 he was appointed President of the Society.
During his years at the Vihara, he has taught courses in Buddhism, conducted
meditation retreats, and lectured widely throughout the United States, Canada,
Europe, Australia and New Zealand.

He has also pursued his scholarly interests by earning a B.A., and M.A., and a
Ph.D. in Philosophy from the American University. He taught courses in Buddhism
at the American University, Georgetown University and University of Maryland.
His books and articles have been published in Malaysia, India, Sri Lanka and the
United States.

Since 1973 he has been buddhist chaplin at The American University counseling
students interested in Buddhism and Buddhist meditation. He is now president of
the Bhavana Society in West Virginia in the Shenandoah Valley, about 100 miles
from Washington, D.C. teaching meditation and conducting meditation retreats.

\newpage
\section*{Preface}

In my experience I found that the most effective way to express something in order to make others understand is to use the
simplest language. Also I learned from teaching that the more rigid the language the less effective it is. People to not respond to
very stern and rigid language especially when we try to teach something which normally people don't engage in during their daily
life. Meditation appears to them as something that they cannot always do. As more people turn to meditation, they need more
simplified instructions so they can practice by themselves without a teacher around. This book is the result of requests made by
many meditators who need a very simple book written in ordinary colloquial language.

In preparing this book I have been helped by many of my friends. I am deeply grateful to all of them. Especially I would like to
express my deepest appreciation and sincere gratitude to John Patticord, Daniel J. Olmsted, Matthew Flickstein, Carol Flickstein,
Patrick Hamilton, Genny Hamilton, Bill Mayne, Bhikkhu Dang Pham Jotika and Bhikkhu Sona for their most valuable
suggestions, comments and criticisms of numerous points in preparing this book. Also thanks to Reverend Sister Sama and Chris
O'Keefe for their support in production efforts.

%Mindfulness In Plain English - Henepola Gunaratana Mahathera
\maketitle

\newpage