\recipe{Jambalaya}
\fromMom

\emph{This easy recipe can be adapted to your tastes by using all green
peppers instead of celery. But celery, onions, and peppers are the holy
trinity of Cajun flavors traditional to jambalaya. When I made it, I
omitted the celery and added red and yellow bell peppers.}

\ingredients
\begin{itemize}
\item 1/2 lb. andouille or spicy pork sausage, cut into pieces
\item 3 stalks celery, chopped
\item 1 lb. boneless skinless chicken thighs, cut into 1" pieces
\item 1 onion, chopped
\item 3 cloves garlic, minced
\item 2 (14 oz.) cans diced tomatoes, undrained
\item 1 Tbsp. sugar
\item 1/8 teaspoon pepper
\item 1 green bell pepper, cut into 1" pieces
\item 1-3 tsp. Tabasco Sauce
\item 1/8 tsp. cayenne pepper
\item 1/2 tsp. dried thyme leaves
\item 1/2 tsp. dried basil leaves
\item 1/2 cup uncooked orzo pasta
\item 1 lb. frozen fully cooked shrimp, thawed
\end{itemize}

\instructions
In medium saucepan, cook sausage until some of the fat is rendered.
Discard fat, and combine sausage with all ingredients except orzo and
shrimp in slow cooker. Cover and cook on LOW for 7 to 9 hours until
chicken is cooked through. Increase heat to HIGH. Stir in orzo, cover
and cook for 15 minutes, or until orzo is tender. Add shrimp, stir,
cover and cook an additional 3-5 minutes until shrimp is heated through.

If you have a new, hotter cooking crockpot check the dish after 5 hours
on low. The pasta should cook in about the same time.
