\recipe{Mexican Casserole}

\ingredients
\begin{itemize}
\item
  1 tablespoon extra-virgin olive oil
\item
  1 pound ground turkey - \emph{or chicken, I used 93\% lean ground
  turkey}
\item
  1 medium yellow onion - \emph{diced}
\item
  1 cup uncooked quinoa
\item
  2 cans red enchilada sauce -- \emph{(10 ounce cans) (mild or medium) or 2 1/2 cups homemade red enchilada sauce}
\item
  1 can black beans -- \emph{(15 ounces), drained and rinsed}
\item
  1 can fire-roasted diced tomatoes in
  their juices -- \emph{(15 ounces)}
\item
  1 cup corn kernels - \emph{fresh or frozen}
\item
  1 red bell pepper - \emph{cored and diced}
\item
  1 green bell pepper - \emph{cored and diced}
\item
  2 tablespoons chili powder
\item
  1 tablespoon ground cumin
\item
  1 teaspoon garlic powder
\item
  1/2 cup water
\item
  1 cup shredded Mexican blend cheese - \emph{divide}
\end{itemize}

\instructions
Heat olive oil in a large skillet over medium high. Add turkey and
onion. Cook and stir about 5 minutes. Transfer to the bottom of a
large slow cooker.

To the slow cooker, add the quinoa, enchilada sauce, black beans,
tomatoes, corn, red bell pepper, green bell pepper, chili powder, cumin,
garlic powder, and 1/2 cup water. Stir to combine, then cover and cook
on high for 2 1/2 to 3 hours or low for 5 to 6 hours, until the liquid
is absorbed and the quinoa is tender.

Remove the lid and stir. Taste and adjust any seasonings as desired.
Stir in 1/2 cup of the shredded cheese, then sprinkle the remaining
cheese over the top. Cover and cook on high until the cheese melts,
about 10 to 15 minutes. Serve hot with any desired toppings.
