\recipe{Zuppa Toscana}

\textit{From C. Howell}\\

This is a much requested recipe on the site given its name! Someone who used to
work at the Olive Garden sent in the original recipe and I've adapted it to
serve just 6-8. Try it since it is really yummy!

It is a very good soup and hits the spot on cold winter days. I've included
this and a few other Olive Garden-inspired recipes on the site for all of our
visitors that enjoy eating at the restaurant chain. In my opinion, making these
recipes at home makes them even better than the ones you eat at the restaurant!
:)

Makes: 6-8 servings

\ingredients
\begin{itemize}
	\item 1 lb ground Italian sausage
	\item 1½ tsp crushed red peppers
	\item 1 large diced white onion
	\item 4 Tbsp bacon pieces
	\item 2 tsp garlic puree
	\item 10 cups water
	\item 5 cubes of chicken bouillon
	\item 1 cup heavy cream (\textit{CH: I do about 16 oz of heavy cream because I prefer it on the creamier side})
	\item 1 lb sliced Russet potatoes, or about 3 large potatoes
	\item ¼ of a bunch of kale (\textit{CH: I use a whole bunch of kale because I love it})
\end{itemize}

\instructions
\begin{enumerate}
	\item Sauté Italian sausage and crushed red pepper in a large pot. Drain excess fat, refrigerate while you prepare other ingredients.
	\item In the same pan, sauté bacon, onions and garlic over low-medium heat for approximately 15 mins. or until the onions are soft.
	\item Add chicken bouillon and water to the pot and heat until it starts to boil.
	\item Add the sliced potatoes and cook until soft, about half an hour.
	\item Add the heavy cream and just cook until thoroughly heated.
	\item Stir in the sausage and the kale, let all heat through and serve. Delicious!
\end{enumerate}

Buon appetito!
