\recipe{Mom's Cilantro-Lime Quinoa Salad}
\fromMom

\ingredients
\begin{itemize}
    \item 1 cup quinoa, rinsed and drained
    \item 1.5  cups veggie broth (or chicky broth or H2O)
    \item 1.5-2 TBS fresh lime juice (have extra on hand…it usually needs it)
    \item 2 cups frozen peas, thawed (no canned peas allowed here)
    \item half cup frozen yellow corn, thawed (once again…no canned stuff)
    \item half small red onion
    \item 0.75 to 1 cup chopped fresh cilantro (include the stems, )
    \item 4 cups mixed greens (no ice bergs allowed here…dark leafy greens or spinach)
    \item 0.25 cup avocado or olive oil
    \item 2 to 3 TBS chipotle or smoky hot sauce of your choice (sauce, not salsa Gringo)
    \item 1 tsp ground cumin (I usually added 2 tsp…or more after it has chilled in the fridge)
    \item 0.25tsp or more chili powder (have the jar available for more after the dish sits and mingles)
    \item 1 tsp garlic powder
    \item 0.25 tsp salt of the sea

\end{itemize}

\instructions
\begin{enumerate}
    \item In a large pot cook quinoa with the broth and lime juice, drain excess liquid and return quinoa to the pot.
\item Stir into the pot the peas, corn, red onion, and cilantro parts. Transfer to a large bowl and allow to chill in the fridge until you are ready to feast.
\item Toss the quinoa mixture with the mixed greens.
\item In a small bowl stir together the oil of choice, hot sauce, cumin, chili powder, garlic powder, and salt. Taste and see if additional spices/oils/lime juice/garlic powder are needed.
\item You can add chopped or shredded chicken and/or feta or cheddar cheese to taste. You can also toss it in a tortilla with some extra hot sauce and chopped tomatoes to make a chilled wrap.
\item Chow and enjoy! Grab a napkin, don't use your sleeve!

\end{enumerate}
