\recipe{Jack Daniel's Chocolate-PeeeeCan Pie}
\fromMom

\ingredients
\begin{itemize}
		\item Prepared pastry dough for one 9-inch pie
		\item 3 extra-large eggs
		\item 2 extra-large egg yolks
		\item \nicefrac{2}{3} cup sugar
		\item \nicefrac{3}{4} cup dark corn syrup
		\item 5 tablespoons butter, melted
		\item $\nicefrac{1}{4}$ cup Jack Daniel´s or other whiskey
		\item \nicefrac{2}{3} cup chopped bittersweet chocolate or semisweet chocolate morsels, divided
		\item 1\nicefrac{1}{4} cups pecan halves or pieces, divided
\end{itemize}

\instructions
\textit{Optional: soak the pecans in whiskey for a couple hours to increase the
flavor.}
\begin{enumerate}
		\item Preheat oven to 350 degrees. Ease pastry dough into a 9-inch pie
				plate. Trim dough and flute edges if desired. Place pie plate
				on a baking sheet.
		\item In a large bowl, whisk together eggs, egg yolks and sugar until
				well combined. Whisk in corn syrup, butter and Jack Daniel´s
				until well blended.
		\item Sprinkle \nicefrac{1}{3} cup of the chocolate pieces over bottom
				of pastry crust. Pour in pie filling. Sprinkle \nicefrac{1}{2}
				cup pecans over filling. Sprinkle remaining \nicefrac{1}{3} cup
				chocolate pieces over, then top with remaining \nicefrac{3}{4}
				cup pecans.
		\item Bake pie 50 to 55 minutes or until set in center. Turn off oven;
				leave pie in the oven with the door closed 15 minutes longer to
				crisp top. Transfer pie to a wire rack; cool at least 2 hours.
		\item If preparing pie a day ahead, cover and refrigerate after cooling
				on rack. For best flavor, let refrigerated pie stand at room
				temperature 1 hour before serving. To serve, cut into small
				wedges; top with ice cream. 
\end{enumerate}
