\recipe{Key Lime Pie}

\textit{Note:} I got this recipe online at \textt{www.browneyedbaker.com/key-lime-pie-recipe/}
\ingredients

For the lime filling
\begin{itemize}
    \item 4 teaspoons grated key lime zest
    \item 4 egg yolks
    \item 14 ounces sweetened condensed milk
    \item \nicefrac{1}{2} cup (114 g) fresh key lime juice
\end{itemize}

For graham cracker crust
\begin{itemize}
    \item 2 cups (200 g) graham cracker crumbs, (approximately 14 full graham crackers)
    \item \nicefrac{1}{3} cup (71 g) light brown sugar
    \item \nicefrac{1}{2} cup (113 g) unsalted butter, melted
    \item pinch salt
\end{itemize}

For the whipped cream topping:
\begin{itemize}
    \item 1 \nicefrac{1}{2} cups (360 ml) heavy cream, chilled
    \item \nicefrac{1}{2} cup (57 g) powdered sugar
    \item \nicefrac{1}{2} teaspoon vanilla extract
\begin{itemize}

\instructions
\begin{enumerate}
    \item Preheat oven to 350 degrees F.
    \item Make the Filling: Whisk the lime zest and egg yolks in a medium bowl
    for 2 minutes. Whisk in the sweetened condensed milk, then the lime juice.
    Set aside at room temperature to thicken while you prepare the crust.
    \item Make the Crust: In a medium bowl, stir together the graham cracker
    crumbs, brown sugar, and salt, ensuring no lumps of brown sugar remain.
    Drizzle the melted butter over the graham cracker mixture and toss to
    combine with a fork, ensuring the mixture is evenly moistened. Press the
    crust mixture evenly into the bottom and sides of a 9-inch pie plate, and
    pack tightly using the back of a measuring cup. Bake for 10 minutes;
    transfer to a wire rack to cool to room temperature.
    \item Once the crust has cooled to room temperature, pour the lime filling
    into the crust. Bake until the center is set yet still wiggly when jiggled,
    15 to 17 minutes. Return the pie to a wire rack; cool to room temperature.
    Refrigerate until well-chilled, at least 3 hours, or overnight.
    \item Make the Whipped Cream: Using an electric mixer, whip the cream on
    medium speed until soft peaks form. At this point, add the powdered sugar, a
    small amount at a time, then the vanilla extract, while continuing to whip
    the cream until stiff peaks form. Decoratively pipe the whipped cream over
    the filling or spread the whipped cream evenly with a spatula. Garnish with
    lime slices, if desired, and serve. Cover leftovers with plastic wrap and
    refrigerate for up to 3 days.
\end{enumerate}

Some notes:
\begin{itemize}
    \item Pan: A 9-inch pie plate is used for this recipe.
    \item Key Lime Juice: If you cannot get fresh key limes, use bottled key
    lime juice for this pie. The recommended brand is Nellie & Joe’s (available
    at most grocery stores). While the flavor will be significantly different,
    you can also use regular limes or a combination of lime and lemon juice.
    \item Key Lime Zest: If you cannot get fresh key limes, you can substitute
    regular lime zest.
    \item Make-Ahea​​​​d: This pie can be made up to 2 days in advance. Wait to
    top with whipped cream until the day you serve it.
    \item How to Store the Pie: Refrigerate the pie, loosely covered with
    plastic wrap, for up to 3 days.
    \item Freezing Instructions: Place the entire pie, uncovered, in the freezer
    until completely frozen. Then wrap well in plastic wrap and then a layer of
    foil (or place in a freezer-safe Ziploc bag) and store in the freezer for up
    to 1 month. Thaw in the refrigerator overnight.

\end{itemize}